The NIR Corn Data Set

### 2019-08-15 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
dissertation add papers table

% usepackage{.} reads in additional LaTeX packages
\usepackage[pdftex]{graphicx}       % to include graphs
\usepackage{natbib}                % A BibTeX style file for references.
\usepackage{amssymb,amsmath}        % for maths symbols and equation numbering
\usepackage{array,tabularx,calc}

@@

	\begin{equation}
	X=TP^T+E 
	\end{equation}
	\begin{equation}
	Y=UQ^T+F
	\end{equation}
	Where T and P are the scoring matrix and the load matrix of the spectral matrix X, respectively. U and Q are the scoring matrix and the load matrix of the detection target vector Y, respectively. E and F are residual matrices of the spectral matrix X and the detection target vector Y, respectively, and T and U can perform linear regression as follows:

@@

	\subsection{Loop times}
	\label{sec:Loop times}
	\subsection{Number of Samples}
	\label{sec:Number of Samples}
	\subsection{Number of Components}
	\label{sec:Number of Components}
	\subsection{Pre-treatment}
	\label{sec:Pre-treatment}
	\subsection{Cross-Validation}
	\label{sec:Cross-Validation}
	\subsection{Compare with papers}
	\label{sec:Compare with papers}
	\section{Conclusions}
	\label{sec:conclution}

	\section{Conclusion}

>>>>

% usepackage{.} reads in additional LaTeX packages
\usepackage[pdftex]{graphicx}       % to include graphs
\usepackage{natbib}                % A BibTeX style file for references.
\usepackage{amssymb,amsmath}        % for maths symbols and equation numbering
\usepackage{array,tabularx,calc}
\usepackage{multirow} % create the tables
\usepackage{lscape} %put table lscape
\usepackage{pdflscape} %put pages lscape

@@

	\begin{equation}
	X=TP^T+E 
	\end{equation}
	\begin{equation}
	Y=UQ^T+F
	\end{equation}
	Where T and P are the scoring matrix and the load matrix of the spectral matrix X, respectively. U and Q are the scoring matrix and the load matrix of the detection target vector Y, respectively. E and F are residual matrices of the spectral matrix X and the detection target vector Y, respectively, and T and U can perform linear regression as follows:
	......

@@

	\subsection{Loop times}
	\label{sec:Loop times}
	\begin{figure}[h]    % start of figure environment
		\centering           % put the graph(s) in the centre of the page (horizontally)
		\includegraphics[width=15.5cm, angle=0]{no_loop_time500.pdf}  % width changes size
		\vspace*{-0.25cm}    % manual adjustment of vertical spacing
		\caption{RMSECV and RMSEP under different loop times}          % a meaningful caption
		\label{fig:looptimes}               % label for the figure
	\end{figure}                        % end of figure environment

	\subsection{Number of Samples}
	\label{sec:Number of Samples}

	\subsection{Number of Components}
	\label{sec:Number of Components}

	\subsection{Pre-treatment}
	\label{sec:Pre-treatment}

	\subsection{Cross-Validation}
	\label{sec:Cross-Validation}

	\subsection{Compare with papers}
	\label{sec:Compare with papers}

	\begin{landscape}
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
	\begin{tabular}{llllllllllll}
		\hline
		\multirow{2}{*}{Paper} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Data\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{Pre-treatment}                                           & \multicolumn{2}{c}{Moisture}    & \multicolumn{2}{c}{Oil}         & \multicolumn{2}{c}{Protein}   & \multicolumn{2}{c}{Starch}    \\ \cline{5-12} 
		&                                                                     &                                                                            &                                                                          & RMSECV         & RMSEP          & RMSECV         & RMSEP          & RMSECV        & RMSEP         & RMSECV        & RMSEP         \\ \hline
		1                      & mp6                                                                 & 60                                                                         & None                                                                     &                & 0.1446034(10)  &                & 0.09225961(10) &               & 0.1400926(10) &               & 0.3436289(10) \\
		2                      & m5                                                                  & 64 5-fold                                                                  & None                                                                     & 0.01488358(10) & 0.02113168(10) &                &                &               &               &               &               \\
		3                      & m5                                                                  & 60                                                                         & SavitzkyGolay                                                            &                & 0.05628462(5)  &                & 0.03163213(12) &               & 0.1085697(6)  &               & 0.2371506(6)  \\
		4                      & m5                                                                  & 40                                                                         & Scale                                                                    &                & 0.05862355(12) &                & 0.3891674(14)  &               & 0.3554446(8)  &               & 0.3878001(9)  \\
		4                      & mp5                                                                 & 40                                                                         & Scale                                                                    &                & 0.4194983(12)  &                & 0.7190886(17)  &               & 0.3731878(8)  &               & 0.4980389(9)  \\
		5                      & mp5                                                                 & 40                                                                         & Scale                                                                    &                & 0.4023674(10)  &                &                &               &               &               &               \\
		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  &                &                & 0.08331678(7)  & 0.07401861(7)  &               &               & 0.3322749(7)  & 0.2890035(7)  \\
		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  &                &                & 0.06403154(7)  & 0.05660701(7)  &               &               & 0.2426438(7)  & 0.2287837(7)  \\
		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(2,2,13)\end{tabular} &                &                & 0.04751603(7)  & 0.03468245(7)  &               &               & 0.3216974(7)  & 0.3037632(7)  \\
		7                      & m5                                                                  & 60                                                                         & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(1,2,21)\end{tabular} &                & 0.04043771(6)  &                & 0.04937681(10) &               & 0.1021954(7)  &               & 0.2630782(5)  \\
		8                      & m5                                                                  & 52                                                                         & Delete 75 , 77                                                           & 0.02177367(10) & 0.0197695(10)  & 0.06621319(10) & 0.05955603(10) & 0.1194857(10) & 0.1123115(10) & 0.2937006(10) & 0.2723313(10)
	\end{tabular}
\end{table}
\end{landscape}

	\begin{landscape}
\begin{table}[]
	\begin{tabular}{lllllllll}
		\hline
		Paper & \begin{tabular}[c]{@{}l@{}}Data\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & Pre-treatment                                                            & \begin{tabular}[c]{@{}l@{}}RMSECV/\\ RMSEP\end{tabular} & Moisture       & Oil            & Protein       & Starch        \\ \hline
		1     & mp6                                                & 60                                                        & None                                                                     & RMSEP                                                   & 0.1446034(10)  & 0.09225961(10) & 0.1400926(10) & 0.3436289(10) \\
		2     & m5                                                 & 64 5-fold                                                 & None                                                                     & RMSECV                                                  & 0.01488358(10) &                &               &               \\
		2     & m5                                                 & 64 5-fold                                                 & None                                                                     & RMSEP                                                   & 0.02113168(10) &                &               &               \\
		3     & m5                                                 & 60                                                        & SavitzkyGolay                                                            & RMSEP                                                   & 0.05628462(5)  & 0.03163213(12) & 0.1085697(6)  & 0.2371506(6)  \\
		4     & m5                                                 & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.05862355(12) & 0.3891674(14)  & 0.3554446(8)  & 0.3878001(9)  \\
		4     & mp5                                                & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.4194983(12)  & 0.7190886(17)  & 0.3731878(8)  & 0.4980389(9)  \\
		5     & mp5                                                & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.4023674(10)  &                &               &               \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  & RMSECV                                                  &                & 0.08331678(7)  &               & 0.3322749(7)  \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  & RMSEP                                                   &                & 0.07401861(7)  &               & 0.2890035(7)  \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  & RMSECV                                                  &                & 0.06403154(7)  &               & 0.2426438(7)  \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  & RMSEP                                                   &                & 0.05660701(7)  &               & 0.2287837(7)  \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(2,2,13)\end{tabular} & RMSECV                                                  &                & 0.04751603(7)  &               & 0.3216974(7)  \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(2,2,13)\end{tabular}  & RMSEP                                                   &                & 0.03468245(7)  &               & 0.3037632(7)  \\
		7     & m5                                                 & 60                                                        & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(1,2,21)\end{tabular} & RMSECV                                                  & 0.04043771(6)  & 0.04937681(10) & 0.1021954(7)  & 0.2630782(5)  \\
		8     & m5                                                 & 52                                                        & Delete 75 , 77                                                           & RMSECV                                                  & 0.02177367(10) & 0.06621319(10) & 0.1194857(10) & 0.2937006(10) \\
		8     & m5                                                 & 52                                                        & Delete 75 , 77                                                           & RMSEP                                                   & 0.0197695(10)  & 0.05955603(10) & 0.1123115(10) & 0.2723313(10)
	\end{tabular}
\end{table}
\end{landscape}

	\section{Conclusions}
	\label{sec:conclution}
